Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes

### 2019-07-03 Paper/AgreementAttraction.Rmd
the ones I miss

<!--
Introduction:
 - Review of the key attraction findings: 
        * English. 
      * German: @ReifegersteEtAl:2016
      * Definitely Russian (Sliosar on gender). [@SlioussarMalko:2016]
      * Arabic: @TuckerEtAl:2015
      * Spanish: @LagoEtAl:2015
      * Turkish: @LagoEtAl:2018
      * Hammerly 2018 [@HammerlyEtAl:2018]
      * @LinzenLeonard:2018
      * @SmithFranck:2018
      * @ParkerPhillips:2017
      * @VasishthEtAl:2017
      * @ReifegersteEtAl:2016
      * @KwonSturt:2016
      * @RisticMolinaroMancini:2016
      * @SlevcMartin:2016
      * @PatsonHusband:2015
      * @Enochson:2015
      * @FranckColonnaRizzi:2015
      * @WagersEtAl:2009
      * Slovak: @BadeckerKuminiak:2007
      * @BockEtAl:2001
      * @FiederEtAl:2014
      * @Staub:2009
      * @TannerNicolBrehm:2014
      * @XiangEtAl:2013
      * @NicenboimEtAl:2018

      @TannerBulkes:2015
      @Staub:2010
      @DankEtAl:2014
      @PearlmutterGarnseyBock:1999
      @FooteBock:2012
      @DillonEtAl:2013

>>>>

<!--
Introduction:
 - Review of the key attraction findings: 
        * English. 
      * German: @ReifegersteEtAl:2016
      * Definitely Russian (Sliosar on gender). [@SlioussarMalko:2016]
      * Arabic: @TuckerEtAl:2015
      * Spanish: @LagoEtAl:2015
      * Turkish: @LagoEtAl:2018
      * Hammerly 2018 [@HammerlyEtAl:2018]
      * @LinzenLeonard:2018
      * @SmithFranck:2018
      * @ParkerPhillips:2017
      * @VasishthEtAl:2017 **
      * @ReifegersteEtAl:2016
      * @KwonSturt:2016
      * @RisticMolinaroMancini:2016
      * @SlevcMartin:2016
      * @PatsonHusband:2015
      * @Enochson:2015 **
      * @FranckColonnaRizzi:2015
      * @WagersEtAl:2009
      * Slovak: @BadeckerKuminiak:2007
      * @BockEtAl:2001
      * @FiederEtAl:2014 **
      * @Staub:2009
      * @TannerNicolBrehm:2014
      * @XiangEtAl:2013
      * @NicenboimEtAl:2018

      @TannerBulkes:2015
      @Staub:2010
      @DankEtAl:2014 **
      @PearlmutterGarnseyBock:1999
      @FooteBock:2012
      @DillonEtAl:2013
